Are populations like a circuit? The relationship between isolation by distance and isolation by resistance

### 2018-10-19 isolation_by_coalescence.tex
proposed rewording of uniqueness section

Since commute times are symmetric, and $R_{zz} = 0$, 
equation \eqref{eqn:R_from_H} provides $n (n-1)/2$ informative equations.
This is larger than $4n$, the number of parameters,
for a grid with at least nine nodes (i.e., $3 \times 3$),
so the system of equations will usually have a unique solution
for grids larger than this, except in special cases.
The same calculation holds for commute times, 
except that (a) we get an additional $n$ equations from the diagonal entries,
but (b) this is counteracted by the additional $n$ coalescence parameters.

>>>>

Since coalescence times are symmetric, 
equation \eqref{eqn:C_matrix} provides $n (n+1)/2$ informative equations.
This is larger than $4n+n$, the number of parameters,
for a grid with at least nine nodes (i.e., $3 \times 3$),
so the system of equations will usually have a unique solution
for grids larger than this, except in special cases.
The same calculation holds for commute times 
except that there are $n$ local diversity parameters instead of $n$ coalescence parameters.
